Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-17 analysis/paper/paper.Rmd
Update to results section description, second paragraph

  It should also be noted that shape variation is not equal along both primary dimensions. 
# Discussion

>>>>

  It should also be noted that shape variation is not equal along both primary dimensions. For flakes in all three dorsal cortex classes, the largest differences between each inter-nested is along the first primary dimension. Slight differences are seen along the second primary dimension, with an increasing amount of variation as one goes from primary to secondary to tertiary flakes, but these changes are minor when compared to the larger changes seen in the first primary dimension. 
# Discussion
